Pricing Games in Heterogeneous Parallel Networks

### 2025-02-09 thesis/slides.tex
Thesis: Pres: Final slides, cleanup, graph and general fixes in all Sections

\subsection{Our model}

@@

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
\begin{center}
	\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
		% Nodes
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

@@

	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$).
\end{frame}

@@

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
\begin{center}
	\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
		% Nodes
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

		% Links
		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
	\end{tikzpicture}
\end{center}
For homogeneous players and tolls $t = (3, 2, 1)$
\[x(t) = \left(\frac15, \frac25, \frac25\right)\]
since $\ell_2(1/2) + t_2 = \ell_3(1/2) + t_3 = 7/2$ and $\ell_1(0) + t_1 = 4$.
\end{frame}

@@

@@

\subsection{Game equivalence}

@@

\subsection{Homogeneous networks}

\begin{frame}{Preliminaries | Homogeneous networks}
	\begin{block}{Flow formula\footcite{Harks_2019}}
		Define $N(t) = \{i \in N | x_i(t) > 0\}$.
		For affine latency functions $\ell_i(x) = a_i x + b_i$, $a_i > 0, b_i \ge 0$ and by solving $\ell_i(x_i) + t_i = K$ with $\sum_{i \in N} x_i = 1$, calculate $K$ and get for all $i \in N$
		\begin{equation*}
			x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
		\end{equation*}
	\end{block}
\end{frame}

\begin{frame}{Preliminaries | Homogeneous networks}
	\begin{block}{Full Wardrop support assumption}
		$x_i(0) > 0$ for all $i \in N$
	\end{block}
	\begin{block}{Pricing N.E. properties\footcite{Harks_2019}}
		$\Pi_i(t)$ is either linear or quadratic, therefore $|B_i(t_{-i})| = 1$.
		If the \textit{full Wardrop support assumption} is satisfied then $t^*$ is unique, $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ and
		\begin{equation*}
			t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
		\end{equation*}
	\end{block}
\end{frame}

%\begin{frame}{Preliminaries | Homogeneous players | Example}
%	\begin{example}
%	\end{example}
%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
%\end{frame}

@@

				% Description
				\node[align=center] at (0.7, -0.8) {$\alpha(p) = p + 1$};
			\end{tikzpicture}
		\end{multicols}
	\end{center}
	\[x(0) = \left(\tfrac23, \tfrac13\right) \qquad \alpha(x_1(0)) = \tfrac53 \quad \alpha(x_2(0)) = \tfrac43\]
\end{frame}

@@

			% Dots
			\fill[black] (0,2/3) ellipse (0.03 and 0.03);
			\draw[black] (0,2/3) ellipse (0.03 and 0.03);
			\node[below left] at (0,2/3) {$\frac23$};
		\end{tikzpicture}
		\caption{Flow function of link operator $1$ of Example}
		\label{figure:alpha_simple:flow_example}
	\end{figure}
\end{frame}

@@

	Also note that 
	\[c_i(p) = c \left(\frac1c \ell_i(x_i) + t_i\right)\]
	where $\frac1c \ell_i(x_i) = \frac{a_i}{c} x_i + \frac{b_i}{c}$ affine.
\end{frame}

@@

\begin{frame}{Heterogeneous Pricing Games}
	Zero money-sensitivity creates issues as it can be exploited.
	\begin{lemma}
		Let $(N, \ell, \alpha)$ where $\alpha(p) = 0$ for $p \in [0, \epsilon]$ for some $\epsilon > 0$.\\
		Then $\exists i \in N$ where $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{n - 1}$.
	\end{lemma}
	\begin{proof}
		Links with $\ell_i(0) = \min_{j \in N} \ell_i(0)$ can select $t_i > \max t_{-i}$ and become the lowest-latency link, with players $\alpha(p) = 0$.

@@

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $([2], \ell, \alpha)$ with
		$
			\alpha(p) =
			\begin{cases}
				1 & p \le \tfrac15 \\
				3 & p \in \left(\tfrac15, \tfrac12\right) \\
				4 & p \ge \tfrac12
			\end{cases}
		$
	\end{example}

	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

@@

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};
			\draw (0,4/5) -- (0.05,4/5) node[right] {$\frac45$};
			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
			\draw (0,1/2) -- (-0.05,1/2) node[left] {$\frac12$};
			\draw (0,1/5) -- (-0.05,1/5) node[left] {$\frac15$};

@@

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};
			\draw (0,3) -- (0.05,3) node[right] {$3$};
			\draw (0,4) -- (-0.05,4) node[left] {$4$};

@@

\begin{frame}{Step distribution functions}
	Let $\Gm_1 = ([2], \ell, \alpha)$ where $\alpha = (\alpha_k)_{k \in [m]}$.
	\begin{lemma}
		Let $t \ne 0$ where all players with $\alpha(p) = \alpha_k$ are using the same link for all $k \in [m]$.
		Then $t$ is not a Nash equilibrium for the pricing game.
	\end{lemma}
	\begin{theorem}
		If $\Gm_1$ has $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ with fixed $\alpha^{(2)}(p) = \as(t^*)$.
		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
	\end{theorem}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
		\begin{align*}
			\alpha(p) =
			\begin{cases}
				3 & p \le \tfrac14 \\
				4 & p > \tfrac14
			\end{cases}&
		\end{align*}
		Then $\Gm$ has a N.E. for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
	\end{example}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=8cm, y=10cm, scale=0.7, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-0.4,0);
			\draw[->] (0,0) -- (0.7,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};

			% Tick marks
			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
			\draw (-1/12,0) -- (-1/12,-0.01) node[left=9,below] {$-\frac{1}{12}$};
			\draw (-1/16,0) -- (-1/16,-0.01) node[right=2,below] {$-\frac{1}{16}$};
			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
			\draw (5/12,0) -- (5/12,-0.01) node[below] {$\frac{5}{12}$};
			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
			\draw (2/3,0) -- (2/3,-0.01) node[below] {$\frac23$};
			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};

			% Pseudo-heterogeneous profits
			\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=17,right=-7,black] {$c = 3$};
			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=10,right=-3,black] {$c = 4$};

			% Profit function
			\draw[thick,domain=-1/3:-1/12] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
			\draw[thick] (-1/12,3/16) -- (-1/16, 39/192);
			\fill[black] (-1/12,3/16) ellipse (0.00625 and 0.005) node[below right] {$\frac{3}{16}$};
			\fill[black] (-1/16,39/192) ellipse (0.00625 and 0.005) node[above left] {$\frac{39}{192}$};
			\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
			\draw[thick] (5/16,31/192) -- (5/12,3/16);
			\fill[black] (5/16,31/192) ellipse (0.00625 and 0.005) node[below left] {$\frac{31}{192}$};
			\fill[black] (5/12,3/16) ellipse (0.00625 and 0.005) node[above right] {$\frac{3}{16}$};
			\draw[thick,domain=5/12:2/3] plot (\x,{((2-3*\x)/3)*(4/12+\x)});

			% Max point
			\fill[red] (1/12, 25/108) ellipse (0.00625 and 0.005) node[below,black] {$\frac{25}{108}$};
		\end{tikzpicture}
		\begin{tikzpicture}[x=10cm, y=15cm, scale=0.7, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-0.55,0);
			\draw[->] (0,0) -- (0.4,0) node[right] {$t_2 - t_1$};
			\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};

			% Tick marks
			%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
			\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
			\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
			\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
			\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_1^* = \frac{5}{12}$};
			\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
			\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
			\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
			\draw (1/3,0) -- (1/3,-0.01) node[below] {$\frac13$};
			%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};

			% Pseudo-heterogeneous profits
			\draw[gray,dashed,thick,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[above=15,right=-7,black] {$c = 3$};
			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};

			% Profit function
			\draw[thick] (-5/12,0) -- (-5/16,5/64);
			\fill[black] (-5/12,0) ellipse (0.0045 and 0.003) node[above left] {$0$};
			\fill[black] (-5/16,5/64) ellipse (0.0045 and 0.003) node[above left] {$\frac{5}{64}$};
			\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
			\draw[thick] (1/16,23/192) -- (1/12,1/8);
			\fill[black] (1/16,23/192) ellipse (0.0045 and 0.003) node[below left] {$\frac{23}{192}$};
			\fill[black] (1/12,1/8) ellipse (0.0045 and 0.003) node[above right] {$\frac18$};
			\draw[thick,domain=1/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)});

			% Max point
			\fill[red] (-1/12, 4/27) ellipse (0.0045 and 0.003) node[above,black] {$\frac{4}{27}$};
		\end{tikzpicture}
		\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$. Red dot indicates the max profit at $t^*$. Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
		\label{figure:alpha_step:profit_ne}
	\end{figure}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
		\begin{align*}
			\alpha(p) =
			\begin{cases}
				2 & p \le \tfrac14 \\
				4 & p > \tfrac14
			\end{cases}&
		\end{align*}
		Then $\Gm$ has no N.E. for the pricing game.
	\end{example}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=6cm, y=10cm, scale=0.7, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-0.4,0);
			\draw[->] (0,0) -- (1.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};

			% Tick marks
			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
			\draw (-1/8,0) -- (-1/8,-0.01) node[left=5,below] {$-\frac18$};
			\draw (-1/16,0) -- (-1/16,-0.01) node[below] {$-\frac{1}{16}$};
			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
			\draw (5/8,0) -- (5/8,-0.01) node[below] {$\frac58$};
			\draw (1,0) -- (1,-0.01) node[below] {$1$};
			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};

			% Pseudo-heterogeneous profits
			\draw[gray,dashed,thick,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 2$};
			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};

>>>>

@@

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
\begin{center}
	\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
		% Nodes
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

@@

	%Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$).
\end{frame}

@@

\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
	\begin{center}
		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
			% Nodes
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

			% Links
			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
			\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
			\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
		\end{tikzpicture}
	\end{center}
	For homogeneous players and tolls $t = (3, 2, 1)$
	\[x(t) = \left(\frac15, \frac25, \frac25\right)\]
	since $\ell_1\left(\frac15\right) + 3 = \ell_2\left(\frac25\right) + 2 = \ell_3\left(\frac25\right) + 1 = \frac{17}{5}$.
\end{frame}

@@

\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
	\begin{block}{Full Wardrop support assumption}
		$x_i(0) > 0$ for all $i \in N$
	\end{block}
	\begin{block}{Pricing N.E. uniqueness\footcite{Harks_2019}}
		If the \textit{full Wardrop support assumption} is satisfied then $t^*$ is unique, $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$.
	\end{block}
\end{frame}

@@

@@

@@

				% Description
				\node[align=center] at (0.7, -0.8) {$\alpha(p) = p + 1$};
			\end{tikzpicture}
		\end{multicols}
	\end{center}
	\[x(0) = \left(\frac23, \frac13\right) \qquad \alpha(x_1(0)) = \frac53 \quad \alpha(x_2(0)) = \frac43\]
\end{frame}

@@

			% Dots
			\fill[black] (0,2/3) ellipse (0.03 and 0.03);
			\draw[black] (0,2/3) ellipse (0.03 and 0.03);
			\node[below left] at (0,2/3) {$\frac23$};
		\end{tikzpicture}
		\caption{Flow function of link $1$ of Example}
		\label{figure:alpha_simple:flow_example}
	\end{figure}
\end{frame}

@@

	Note that 
	\[c_i(p) = c \left(\frac1c \ell_i(x_i) + t_i\right)\]
	where $\frac1c \ell_i(x_i) = \frac{a_i}{c} x_i + \frac{b_i}{c}$ affine.
\end{frame}

@@

\begin{frame}{Zero money-sensitivity}
	Zero money-sensitivity creates issues as it can be exploited.
	\begin{lemma}
		Let $(N, \ell, \alpha)$ where $\alpha(p) = 0$ for $p \in [0, \epsilon]$ for some $\epsilon > 0$.\\
		Then $\exists i \in N$ where $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{n - 1}$.
	\end{lemma}
	\begin{proof}
		Links with $\ell_i(0) = \min_{j \in N} \ell_i(0)$ can select $t_i > \max t_{-i}$ and become the lowest-latency link, with players $\alpha(p) = 0$.

@@

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $([2], \ell, \alpha)$ with
		$
			\alpha(p) =
			\begin{cases}
				1 & p \le \tfrac15 \\
				3 & p \in \left(\tfrac15, \tfrac12\right) \\
				4 & p \ge \tfrac12
			\end{cases}
		$
	\end{example}
	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

@@

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-2/5,0) -- (-2/5,-0.05) node[left=4,below] {$-\frac25$};
			\draw (-2/15,0) -- (-2/15,-0.05) node[left=4,below] {$-\frac{2}{15}$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (1/8,0) -- (1/8,-0.05) node[left=1,below] {$\frac18$};
			\draw (1/6,0) -- (1/6,-0.05) node[right=2,below] {$\frac16$};
			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};
			\draw (0,4/5) -- (0.05,4/5) node[right] {$\frac45$};
			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
			\draw (0,1/2) -- (-0.05,1/2) node[left] {$\frac12$};
			\draw (0,1/5) -- (-0.05,1/5) node[left] {$\frac15$};

@@

			% Tick marks
			\draw (-1,0) -- (-1,-0.2) node[below] {$-1$};
			\draw (-2/5,0) -- (-2/5,-0.2) node[left=4,below] {$-\frac25$};
			\draw (-2/15,0) -- (-2/15,-0.2) node[left=4,below] {$-\frac{2}{15}$};
			\draw (0,0) -- (0,-0.2) node[below] {$t_2$};
			\draw (1/8,0) -- (1/8,-0.2) node[left=1,below] {$\frac18$};
			\draw (1/6,0) -- (1/6,-0.2) node[right=2,below] {$\frac16$};
			\draw (7/15,0) -- (7/15,-0.2) node[below] {$\frac{7}{15}$};
			\draw (7/5,0) -- (7/5,-0.2) node[below] {$\frac75$};
			\draw (2,0) -- (2,-0.2) node[below] {$2$};
			\draw (0,1) -- (-0.08,1) node[left=1] {$1$};
			\draw (0,3) node[right=1] {$3$} -- (0.05,3);
			\draw (0,4) -- (-0.08,4) node[left=1] {$4$};

@@

\begin{frame}{Step distribution functions}
	Let $\Gm_1 = ([2], \ell, \alpha)$ where $\alpha = (\alpha_k)_{k \in [m]}$.
	\begin{lemma}
		Let $t \ne 0$ where all players with $\alpha(p) = \alpha_k$ are using the same link for all $k \in [m]$.
		Then $t$ is not a Nash equilibrium for the pricing game.
	\end{lemma}
	\begin{theorem}
		If $\Gm_1$ has $t^*$, let $\Gm_2 = ([2], \ell, \alpha^{(2)})$ with fixed $\alpha^{(2)}(p) = \as(t^*)$.
		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
	\end{theorem}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $\Gm = ([2], \ell, \alpha)$ where
		$
			\alpha(p) =
			\begin{cases}
				3 & p \le \tfrac14 \\
				4 & p > \tfrac14
			\end{cases}
		$.\\
		Then $\Gm$ has a N.E. for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
	\end{example}
	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

				% Tick marks
				\draw (0,0) -- (0,-0.05) node[below] {$0$};
				\draw (0.25,0) -- (0.25,-0.05) node[below] {$\frac14$};
				\draw (1,0) -- (1,-0.05) node[below] {$1$};
				\draw (0,3) -- (-0.05,3) node[left] {$3$};
				\draw (0,4) -- (-0.05,4) node[left] {$4$};

				% Function graph
				\draw[thick] (0,3) -- (0.25,3);
				\draw[thick] (0.25,4) -- (1,4);

				% Closed / Open dots
				\fill[black] (0.25,3) ellipse (0.014 and 0.06);
				\draw[black] (0.25,3) ellipse (0.014 and 0.06);
				\fill[white] (0.25,4) ellipse (0.014 and 0.06);
				\draw[black] (0.25,4) ellipse (0.014 and 0.06);
			\end{tikzpicture}
		\end{multicols}
	\end{center}
\end{frame}

\begin{frame}{Step distribution functions}
	If $t^*$ exists, it needs to be at $\as(t^*) = 3$ or $4$.

	Flow will be the same regardless.

	Assume $\Gm^\prime = (N, \ell, 1)$ and we calculate
	\[t^{*\prime} = \left(\frac53, \frac43\right) \qquad x(t^*) = \left(\frac59, \frac49\right)\]

	Since $t_1 > t_2$, link $1$ has the lower split, so the split is at $\alpha\left(\frac59\right) = 4$.

	Candidate Pricing N.E.:
	\[t^* = \frac14 t^{*\prime} = \left(\frac{5}{12}, \frac{4}{12}\right)\]
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=8cm, y=10cm, scale=0.7, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-0.4,0);
			\draw[->] (0,0) -- (0.7,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1\left(t_1, \frac{4}{12}\right)$};

			% Tick marks
			\draw (-1/3,0) -- (-1/3,-0.015) node[left=4,below] {$-\frac13$};
			\draw (-1/4,0) -- (-1/4,-0.015) node[left=4,below] {$-\frac14$};
			\draw (-1/12,0) -- (-1/12,-0.015) node[left=9,below] {$-\frac{1}{12}$};
			\draw (-1/16,0) -- (-1/16,-0.015) node[right=4,below] {$-\frac{1}{16}$};
			%\draw (0,0) -- (0,-0.015) node[below] {$0$};
			\draw (1/12,0) -- (1/12,-0.015) node[below] {$\frac{1}{12}$};
			\draw (5/16,0) -- (5/16,-0.015) node[below] {$\frac{5}{16}$};
			\draw (5/12,0) -- (5/12,-0.015) node[below] {$\frac{5}{12}$};
			\draw (2/4,0) -- (2/4,-0.015) node[below] {$\frac24$};
			\draw (2/3,0) -- (2/3,-0.015) node[below] {$\frac23$};

			% Pseudo-heterogeneous profits
			\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[right=3,above=8,black] {$c = 3$};
			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[left=23,above=1,black] {$c = 4$};

			% Profit function
			\draw[thick,domain=-1/3:-1/12] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
			\draw[thick] (-1/12,3/16) -- (-1/16, 39/192);
			\fill[black] (-1/12,3/16) ellipse (0.00625 and 0.005) node[right=2,below=-1] {$\frac{3}{16}$};
			\fill[black] (-1/16,39/192) ellipse (0.00625 and 0.005) node[left=7,above=-1] {$\frac{39}{192}$};
			\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
			\draw[thick] (5/16,31/192) -- (5/12,3/16);
			\fill[black] (5/16,31/192) ellipse (0.00625 and 0.005) node[left=7,below=-3] {$\frac{31}{192}$};
			\fill[black] (5/12,3/16) ellipse (0.00625 and 0.005) node[right=7,above=-1] {$\frac{3}{16}$};
			\draw[thick,domain=5/12:2/3] plot (\x,{((2-3*\x)/3)*(4/12+\x)});

			% Max point
			\fill[red] (1/12, 25/108) ellipse (0.00625 and 0.005) node[below,black] {$\frac{25}{108}$};
		\end{tikzpicture}
		\\[6pt]
		\begin{tikzpicture}[x=10cm, y=15cm, scale=0.7, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-0.55,0);
			\draw[->] (0,0) -- (0.4,0) node[right] {$t_2 - t_1$};
			\draw[->] (0,0) -- (0,0.215) node[above] {$\Pi_2\left(\frac{5}{12}, t_2\right)$};

			% Tick marks
			%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
			\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
			\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
			\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
			\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
			\draw (0,0) -- (0,-0.01) node[below] {$0$};
			\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
			\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
			\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
			\draw (1/3,0) -- (1/3,-0.01) node[below] {$\frac13$};
			%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};

			% Pseudo-heterogeneous profits
			\draw[gray,dashed,thick,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[right=3,above=8,black] {$c = 3$};
			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[left=23,above=1,black] {$c = 4$};

			% Profit function
			\draw[thick] (-5/12,0) -- (-5/16,5/64);
			\fill[black] (-5/12,0) ellipse (0.0045 and 0.003) node[left=4,above=-1] {$0$};
			\fill[black] (-5/16,5/64) ellipse (0.0045 and 0.003) node[left=4,above=-1] {$\frac{5}{64}$};
			\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
			\draw[thick] (1/16,23/192) -- (1/12,1/8);
			\fill[black] (1/16,23/192) ellipse (0.0045 and 0.003) node[left=4,below=-1] {$\frac{23}{192}$};
			\fill[black] (1/12,1/8) ellipse (0.0045 and 0.003) node[right=4,above=-1] {$\frac18$};
			\draw[thick,domain=1/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)});

			% Max point
			\fill[red] (-1/12, 4/27) ellipse (0.0045 and 0.003) node[above,black] {$\frac{4}{27}$};
		\end{tikzpicture}
		%\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$. Red dot indicates the max profit at $t^*$. Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
		%\label{figure:alpha_step:profit_ne}
	\end{figure}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $\Gm = ([2], \ell, \alpha)$ where
		$
			\alpha(p) =
			\begin{cases}
				2 & p \le \tfrac14 \\
				4 & p > \tfrac14
			\end{cases}
		$.\\
		Then $\Gm$ has no N.E. for the pricing game.
	\end{example}
	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
